---
title: "Lec12"
author: "HO Yin Shan"
date: "2023-04-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = F,
                      warning = F)
library(tidyverse)
```


```{r}
retail <- read.csv("retail_sales.csv")
attach(retail)
```

1. Use simple regression to predict sales using Market.

```{r}
model = lm(Sales ~ Market)
summary(model)
```

2. What are the predicted sales in each of the three
markets?   

Sales = 347.31 + 83.16 * MarketSuburban + 190.04 * MarketUrban   

3. How to interpret the coefficients?   

Rural = 347.31
Suburban = 347.31 + 83.16
Urban = 347.31 + 190.04 

4. Is the difference in sales between different markets
significant?   
From the summary, the p-value is very small which indicate it is significant.

5. Make a scatterplot (sales vs. income) of the three
groups of Market. Add the legend to the plot.

```{r}
retail %>% 
  ggplot(aes(x = Income, y = Sales, color = Market)) +
  geom_point()+
# facet_wrap(~Market)+
  theme_classic()
```

```{r}
model1 = lm(Sales~ Income + Market + Income*Market)
summary(model1)
```

Sales = -172.694 + Income * 8.313 + MarketSuburban * 418.245 + MarketUrban * 441.399 - Income * MarketSuburban * 5.997 - Income * MarketUrban * 4.516   

Rural: Sales = -172.694 + 418.245 + (8.313 - 5.997) * Income   
Rural: Sales = -172.694 + 441.399 + (8.313 - 4.516) * Income   

```{r}
newcase = data.frame(Income = 72, Market = "Urban")
predict(model1, newcase)
```

```{r}
retail %>% 
  ggplot(aes(x = Income, y = Sales, color = Market)) +
  geom_point()+
 #facet_wrap(~Market, ncol = 1)+
  theme_classic()+
  geom_smooth(method = "lm" , se = F)
```


```{r}
summary(model1)
```

Because p-value of MarketSuburban is 0.05988 which is greater than 0.05. Therefore it is statistically indifferent to 0 as it is statistically random variable.


#################################################

```{r}
movies <- read.csv("movies.csv")
attach(movies)
```

```{r}
plot(Profit ~ LOpening)

f = lm(Profit ~ LOpening)
summary(f)
```

```{r}
logit <- glm(Profit~LOpening, family="binomial")

summary(logit)
```

log(p/1-p) = -3.1656 + 1.3082 * LOpening

newmovie = 4

log(p/1-p) = -3.1656 + 1.3082 * 4 = 2.067197

e^2.067197/(1+e^2.067197) = 0.8876738

```{r}
newmovie = data.frame(LOpening = 4)
predict(logit, newmovie, type = "response")
```

```{r}
plot(LOpening, Profit)
predicted = predict(logit, movies, type = "response")
points(LOpening, predicted, col = 2, pch =2)
```

```{r}
logit1 <- glm(Profit ~ LOpening + Theaters + Opinion, family = "binomial") 
summary(logit1)
```


```{r}
pchisq(47.111 - 34.396, 34-31, lower.tail = F)
```


2. When there is 1 unit increase in LOpening, there will be 2.1463588 increase in log odds.

```{r}
logit2 <- update(logit1, .~. - Opinion) 
  summary(logit2)
```

```{r}
# calcuating p-value
pchisq(47.111 - 34.455, 34-32, lower.tail = F)
```

```{r}
logit3 <- update(logit1, .~. - Opinion - Theaters) 
  summary(logit3)
```

```{r}
# calcuating p-value
pchisq(47.111 - 35.708, 34-33, lower.tail = F)
```

###########################################

```{r}
flight <- read.csv("FlightDelays.csv")
attach(flight)
```

```{r}
flight <- flight %>% 
  mutate(schedtime = as.factor(schedtime),
         dayweek = as.factor(dayweek)) %>% 
  select(-date, -flightnumber, -daymonth, -distance)
```

```{r}
flightlogit <- glm(delay~., data = flight, family = "binomial")  
  summary(flightlogit)
```

```{r}
# scheduletime and dayweek are categorical variables!!! use " " 
newflight = data.frame(dest = "EWR", origin = "IAD", carrier= "UA", schedtime = "15", weather = 0, dayweek = "2")
predict(flightlogit, newflight, type = "response")
```


