---
title: "Lec10"
author: "HO Yin Shan"
date: "2023-03-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
library(tidyverse)
library(ggfortify)
```


```{r}
subprime1 <- read_csv("subprime1.csv")
```

# Lec9 (13th Slides p18)

Q1. Examine the relationship between each pair of variables numerically and visually.

```{r}
cor(subprime1)
```

```{r}
plot(subprime1)
```
Q2. Fit a multiple regression model using all the variables to predict APR. Name the model g. Write down the fitted linear model.

```{r}
g <- lm(APR ~ LTV + FICO + `Stated Income` + `Home Value`, data = subprime1)
summary(g)
```

APR = 23.7253652432 - 1.5888429952* LTV - 0.0184317607* FICO + 0.0004032124* Stated Income - 0.0007520823 *Home Value


Q3. Make a residual plot of **ð‘’** on **ð‘Œ_bar**.

```{r}
plot(g$fitted, g$residuals)
```

Q4. Make a residual plot of **ð‘’** on **FICO**.

```{r}
plot(subprime1$FICO, g$residuals)
```
Q5. Make a normal quantile plot of residuals (including the straight line) 

```{r}
#method 1
autoplot(g)

#method 2 
qqnorm(g$residuals)
qqline(g$residuals)
```

Q6. Make a histogram of the residuals.

```{r}
hist(g$residuals)
```
Q7. Does the four variables together explain statistically significant variation in APR?

```{r}
summary(g)
# check F statistics (questions asked 4 variables together)
```

p-value: < 2.2e-16, for the whole model **(four variables together)**, the model is statistically significant.


Q8. Is the effect of *Stated.Income* significant, given the values of the other three variables?

No, because p-value is 0.9036.



# Lec10

```{r}
capm <- read_csv("capm.csv")
retail <- read_csv("retail_prof.csv")
```



